Exploring dimensions of biodiversity in Japanese ferns

### 2021-05-28 ms/manuscript.Rmd
Remove colformat_md()
for some very weird reason, it was causing pandoc to not be able to find references.yaml. See error produced in last commit:

Could not find bibliography file: references.yaml
Error running filter /usr/local/bin/pandoc-citeproc:
Filter returned error status 1
Quitting from lines 641-649 (manuscript.Rmd)

```{r env-model-params-doc, results = "asis", eval = params$doc_type == "doc"}
env_model_params_pretty %>%
  mutate(
    across(where(is.numeric), as.character)) %>%
  rename("*t*-value" = t_value, "*p*-value" = p_value, "Variable" = term, "Estimate" = estimate, "Conditional SE" = cond_se) %>%
  as_grouped_data(groups = "resp_var") %>%
  as_flextable(hide_grouplabel = TRUE, col_keys = c("Variable", "Estimate", "Conditional SE", "*t*-value", "*p*-value")) %>%
  bold(i = ~ signif == TRUE, bold = TRUE) %>%
  colformat_md(part = "header")
```

>>>>

```{r env-model-params-doc, results = "asis", eval = params$doc_type == "doc"}
env_model_params_pretty %>%
  mutate(
    across(where(is.numeric), as.character)) %>%
  rename("*t*-value" = t_value, "*p*-value" = p_value, "Variable" = term, "Estimate" = estimate, "Conditional SE" = cond_se) %>%
  as_grouped_data(groups = "resp_var") %>%
  as_flextable(hide_grouplabel = TRUE, col_keys = c("Variable", "Estimate", "Conditional SE", "*t*-value", "*p*-value")) %>%
  bold(i = ~ signif == TRUE, bold = TRUE)
```
